---
title: "Weight of Fish"
author: "Madeleine Alseryani"
date: "Spring 2022"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
Fish<-read.csv(file = "Fish.csv")
```

# Predicting Fish Weight


## Perch

```{r}
Perch<- filter(Fish, Species == "Perch")
Perch = subset(Perch, select = -Species)
```



### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```

### Best Two regressor model

From this Model, we can see that the best two regressor models are the ones which include height and weight. It also has an adjusted R squared value of 0.94 making it the best model.

## Pike

```{r}
Pike<- filter(Fish, Species == "Pike")
Pike = subset(Pike, select = -Species)
```

### Best Models

```{r}
Perch<- filter(Fish, Species == "Perch")
Perch = subset(Perch, select = -Species)
```



### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",
legend="bottomright",main="Adjusted R^2")
```

### Best Two regressor model

From this model we can see that the best two regressor models are Length 1 and length 3.

## Roach

```{r}
Roach<- filter(Fish, Species == "Roach")
Roach = subset(Roach, select = -Species)
```

### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",
legend="bottomleft",main="Adjusted R^2")
```

### Best Two regressor model

From this model, we can see that the two best regressor models are length 3 and Width. It is also the best model overall. By looking at it, we can see that it is the highest.

## Final Summary Statements

In conclusion, we can see that the first model (pirch) and the last model were the best two regressor models. This exercise showed me how to find multiple regression results. 